CF Registry Analysis

### 2022-11-02 Christine Chan/CF Registry/cf_registry_analysis.Rmd
registry analysis formatting

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(performance)
library(knitr)
library(parallel)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = "/Users/timvigers/Documents/Work/CF/Christine Chan/CF Registry")
```

```{r}
# Read in CSVs
df <- read.csv("./Data_Raw/CFF19_encountersMerged_Del1.csv")
annual <- read.csv("./Data_Raw/CFF19_Annualized_Del1.csv")
colnames(annual)[colnames(annual) == "ReviewYear"] <- "reviewyear"
demo <- read.csv("./Data_Raw/CFF19_DemogCFDiag_Del1.csv")
# Combine and format demographics columns
demo$Race <- apply(demo, 1, function(r) {
  race <- r[paste0("Race", 1:6)]
  race <- as.numeric(which(race == 1))
  race <- paste(race, collapse = ", ")
})
demo$Race[grep(", ", demo$Race)] <- "More Than One"
demo$Race <- factor(demo$Race,
  levels = c(1:6, "More Than One"),
  labels = c(
    "White", "Black or African American",
    "American Indian or Alaska Native", "Asian",
    "Native Hawaiian or Other Pacific Islander",
    "Some other race", "More Than One"
  )
)
demo$Hispanicrace <- factor(demo$Hispanicrace,
  levels = 1:2,
  labels = c("Yes", "No")
)
# Merge
df <- left_join(df, annual, by = c("eDWID", "reviewyear"))
df <- left_join(df, demo, by = "eDWID")
# Group years by 2003-2009, 2010-2013, and 2014-2018
df$Period <- cut(df$reviewyear,
  breaks = c(2002, 2009, 2013, 2018),
  labels = c("2003 - 2009", "2010 - 2013", "2014 - 2018")
)
df$smoking <- factor(df$smoking, levels = 1:4, labels = c(
  "No",
  "Occasionally",
  "Yes, Regularly, less than 1 ppd",
  "Yes, Regularly, 1 ppd or more"
), ordered = T)
df$second_smoke <- factor(df$smoking, levels = 1:4, labels = c(
  "No",
  "Occasionally",
  "Yes, Regularly, less than 1 ppd",
  "Yes, Regularly, 1 ppd or more"
), ordered = T)
# Factors
ed_levels <- c(
  "Less than High School",
  "High School diploma or equivalent",
  "Some College",
  "College Graduate",
  "Masters/Doctoral level degree"
)
df$patient_education <- factor(df$patient_education,
  levels = c(1:5),
  labels = ed_levels
)
df$father_education <- factor(df$father_education,
  levels = c(1:5),
  labels = ed_levels
)
df$mother_education <- factor(df$mother_education,
  levels = c(1:5),
  labels = ed_levels
)
df$spouse_education <- factor(df$spouse_education,
  levels = c(1:5),
  labels = ed_levels
)
df$pregnant <- factor(df$pregnant, levels = 0:1, labels = c("No", "Yes"), ordered = T)
# Combine education checkboxes
cl <- makeCluster(detectCores() * 0.5, type = "FORK")
df$employment <- parApply(cl, df, 1, function(r) {
  emp <- r[paste0("employment", 1:7)]
  emp <- as.numeric(emp)
  if (all(is.na(emp) | emp == 0)) {
    return(NA)
  } else {
    emp <- as.numeric(emp)
    emp <- which(emp == 1)
    emp <- paste(emp, collapse = ", ")
    return(emp)
  }
})
stopCluster(cl)
df$employment <- sub("1", "Part Time", df$employment)
df$employment <- sub("2", "Full time homemaker", df$employment)
df$employment <- sub("3", "Full time employment", df$employment)
df$employment <- sub("4", "Unemployed", df$employment)
df$employment <- sub("5", "Student", df$employment)
df$employment <- sub("6", "Disabled", df$employment)
df$employment <- sub("7", "Retired", df$employment)
df$employment <- as.factor(df$employment)
# Small dataframe for checking
test <- df[1:1000, ]
write.csv(test, "~/test.csv", row.names = F, na = "")
```

>>>>

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(performance)
library(knitr)
library(parallel)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = "~/Dropbox/Work/CHCO/Christine Chan/CF registry data")
```

```{r eval=FALSE}
# Read in CSVs
df <- read.csv("CFF19_encountersMerged_Del1.csv")
annual <- read.csv("CFF19_Annualized_Del1.csv")
colnames(annual)[colnames(annual) == "ReviewYear"] <- "reviewyear"
demo <- read.csv("CFF19_DemogCFDiag_Del1.csv")
# Combine and format demographics columns
demo$Race <- apply(demo, 1, function(r) {
  race <- r[paste0("Race", 1:6)]
  race <- as.numeric(which(race == 1))
  race <- paste(race, collapse = ", ")
})
demo$Race[grep(", ", demo$Race)] <- "More Than One"
demo$Race <- factor(demo$Race,
  levels = c(1:6, "More Than One"),
  labels = c(
    "White", "Black or African American",
    "American Indian or Alaska Native", "Asian",
    "Native Hawaiian or Other Pacific Islander",
    "Some other race", "More Than One"
  )
)
demo$Hispanicrace <- factor(demo$Hispanicrace,
  levels = 1:2,
  labels = c("Yes", "No")
)
# Merge
df <- left_join(df, annual, by = c("eDWID", "reviewyear"))
df <- left_join(df, demo, by = "eDWID")
# Group years by 2003-2009, 2010-2013, and 2014-2018
df$Period <- cut(df$reviewyear,
  breaks = c(2002, 2009, 2013, 2018),
  labels = c("2003 - 2009", "2010 - 2013", "2014 - 2018")
)
df$smoking <- factor(df$smoking, levels = 1:4, labels = c(
  "No",
  "Occasionally",
  "Yes, Regularly, less than 1 ppd",
  "Yes, Regularly, 1 ppd or more"
), ordered = T)
df$second_smoke <- factor(df$smoking, levels = 1:4, labels = c(
  "No",
  "Occasionally",
  "Yes, Regularly, less than 1 ppd",
  "Yes, Regularly, 1 ppd or more"
), ordered = T)
# Factors
ed_levels <- c(
  "Less than High School",
  "High School diploma or equivalent",
  "Some College",
  "College Graduate",
  "Masters/Doctoral level degree"
)
df$patient_education <- factor(df$patient_education,
  levels = c(1:5),
  labels = ed_levels
)
df$father_education <- factor(df$father_education,
  levels = c(1:5),
  labels = ed_levels
)
df$mother_education <- factor(df$mother_education,
  levels = c(1:5),
  labels = ed_levels
)
df$spouse_education <- factor(df$spouse_education,
  levels = c(1:5),
  labels = ed_levels
)
df$pregnant <- factor(df$pregnant, levels = 0:1, labels = c("No", "Yes"), ordered = T)
# Combine education checkboxes
cl <- makeCluster(detectCores() * 0.5, type = "FORK")
df$employment <- parApply(cl, df, 1, function(r) {
  emp <- r[paste0("employment", 1:7)]
  emp <- as.numeric(emp)
  if (all(is.na(emp) | emp == 0)) {
    return(NA)
  } else {
    emp <- as.numeric(emp)
    emp <- which(emp == 1)
    emp <- paste(emp, collapse = ", ")
    return(emp)
  }
})
stopCluster(cl)
df$employment <- sub("1", "Part Time", df$employment)
df$employment <- sub("2", "Full time homemaker", df$employment)
df$employment <- sub("3", "Full time employment", df$employment)
df$employment <- sub("4", "Unemployed", df$employment)
df$employment <- sub("5", "Student", df$employment)
df$employment <- sub("6", "Disabled", df$employment)
df$employment <- sub("7", "Retired", df$employment)
df$employment <- as.factor(df$employment)
# Save formatted data for re-import later
save(df,file = "formatted_data.Rdata")
```

```{r}
load("formatted_data.Rdata")
```
